Enhancement of SDR in Thessaloniki

### 2024-02-28 GHI_enh_03_process.tex
Commit 2024-02-28 16:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-27}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-382.05 -149.78  -46.64   98.42  770.22

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -1.067e+02  5.109e+01  -2.088   0.0375 *  
as.numeric(Date)  3.393e-07  4.098e-08   8.279  2.5e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 216.2 on 358 degrees of freedom
Multiple R-squared:  0.1607,    Adjusted R-squared:  0.1583 
F-statistic: 68.54 on 1 and 358 DF,  p-value: 2.498e-15
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-382.05 -149.78  -46.64   98.42  770.22

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -1.067e+02  5.109e+01  -2.088   0.0375 *  
ST_E_monthly$Date  3.393e-07  4.098e-08   8.279  2.5e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 216.2 on 358 degrees of freedom
Multiple R-squared:  0.1607,    Adjusted R-squared:  0.1583 
F-statistic: 68.54 on 1 and 358 DF,  p-value: 2.498e-15
\end{verbatim}

@@

\begin{verbatim}
2024-02-27 11:14:26.8 athan@sagan GHI_enh_03_process.R 1.108372 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-28}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

\begin{verbatim}
2024-02-28 13:08:22.6 athan@sagan GHI_enh_03_process.R 1.133646 mins
\end{verbatim}

### 2024-02-28 GHI_enh_04_investigate.tex
Commit 2024-02-28 16:14

lmD: 1.608404 +/- 0.1098661

lmY: 1.608426 +/- 0.1098682

Arima: 1.6087 0.1487 10.8185 0

@@

lmD: 1.06616 +/- 0.1703576

lmY: 1.066188 +/- 0.1703608

Arima: 1.1439 0.255 4.4864 0

lmD: 0.2020422 +/- 0.1403033

lmY: 0.2020754 +/- 0.140306

@@

Arima: 0.2014 5.4204 0.0371 0.9704

@@

lmD: 499.5958 +/- 96.35149

lmY: 499.601 +/- 96.35332

Arima: 500.7839 150.1232 3.3358 9e-04

@@

lmD: 0.003319458 +/- 0.0002745369

lmY: 0.003319501 +/- 0.0002745421

Arima: 0.0033 4e-04 9.0564 0

@@

lmD: 0.001746196 +/- 0.0003178251

lmY: 0.001746269 +/- 0.0003178311

Arima: 0.0019 5e-04 3.7071 2e-04

lmD: 0.2020422 +/- 0.1403033

lmY: 0.2020754 +/- 0.140306

@@

lmD: 0.9305909 +/- 0.1460762

lmY: 0.9306112 +/- 0.146079

Arima: 1.0003 0.2219 4.5077 0

@@

lmD: 0.8634408 +/- 0.1045511

lmY: 0.8634567 +/- 0.1045531

Arima: 0.8634 0.1212 7.1257 0

@@

lmD: 0.1926088 +/- 0.038164

lmY: 0.1926139 +/- 0.03816473

Arima: 0.1926 0.0403 4.7782 0

@@

lmD: 0.5100905 +/- 0.04695669

lmY: 0.5100995 +/- 0.04695759

Arima: 0.5101 0.0557 9.1553 0

@@

lmD: 25.65919 +/- 2.576134

lmY: 25.65971 +/- 2.576183

Arima: 25.6594 3.1045 8.2652 0

@@

lmD: 0.001358275 +/- 0.0001381135

lmY: 0.001358294 +/- 0.0001381161

Arima: 0.0014 2e-04 8.5635 0

@@

lmD: 0.0003544276 +/- 6.15321e-05

lmY: 0.0003544331 +/- 6.153328e-05

Arima: 4e-04 1e-04 5.1881 0

@@

lmD: 0.03803985 +/- 0.003667512

lmY: 0.03804065 +/- 0.003667582

Arima: 0.038 0.0043 8.9476 0

@@

lmD: 0.2175113 +/- 0.2519978

lmY: 0.217552 +/- 0.2520021

Arima: 0.2071 0.368 0.5628 0.5736

@@

lmD: 0.1126483 +/- 0.193195

lmY: 0.112674 +/- 0.1931983

Arima: 0.0865 0.3384 0.2558 0.7981

@@

lmD: 0.02925782 +/- 0.02144818

lmY: 0.02925974 +/- 0.02144855

Arima: 0.0293 0.0223 1.3139 0.1889

@@

lmD: 6.106963 +/- 4.268209

lmY: 6.107414 +/- 4.268282

Arima: 6.107 4.3537 1.4027 0.1607

@@

lmD: 0.0004829553 +/- 0.0002839705

lmY: 0.0004829612 +/- 0.0002839754

Arima: 5e-04 3e-04 1.492 0.1357

@@

lmD: 0.000372236 +/- 0.0002233382

lmY: 0.0003722343 +/- 0.0002233421

Arima: 4e-04 3e-04 1.3298 0.1836

@@

lmD: 0.008401207 +/- 0.005558251

lmY: 0.008401691 +/- 0.005558346

Arima: 0.0084 0.0058 1.453 0.1462

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-36} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-39} \end{center}

@@

\begin{verbatim}
2024-02-27 10:55:58.9 athan@tyler GHI_enh_04_investigate.R 0.609646 mins
\end{verbatim}

>>>>

lmD: 1.566022 +/- 0.1083205

lmY: 1.566038 +/- 0.1083224

Arima: 1.5664 0.1467 10.6787 0

@@

lmD: 1.087008 +/- 0.1678713

lmY: 1.087035 +/- 0.1678742

Arima: 1.16 0.2511 4.6199 0

lmD: -0.01234536 +/- 0.1388793

lmY: -0.01233011 +/- 0.1388818

@@

Arima: -0.0132 6.8981 -0.0019 0.9985

@@

lmD: 561.0124 +/- 94.87888

lmY: 561.0217 +/- 94.88053

Arima: 562.031 148.2404 3.7913 1e-04

@@

lmD: 0.003266094 +/- 0.0002706818

lmY: 0.003266127 +/- 0.0002706866

Arima: 0.0033 4e-04 9.0498 0

@@

lmD: 0.001677055 +/- 0.00031363

lmY: 0.001677118 +/- 0.0003136354

Arima: 0.0018 5e-04 3.6151 3e-04

lmD: -0.01234536 +/- 0.1388793

lmY: -0.01233011 +/- 0.1388818

@@

lmD: 0.9770213 +/- 0.1439346

lmY: 0.9770437 +/- 0.1439371

Arima: 1.041 0.2186 4.7612 0

@@

lmD: 0.8175146 +/- 0.1034317

lmY: 0.8175255 +/- 0.1034336

Arima: 0.8175 0.12 6.8104 0

@@

lmD: 0.1909484 +/- 0.03787569

lmY: 0.190953 +/- 0.03787636

Arima: 0.191 0.0401 4.7635 0

@@

lmD: 0.4856759 +/- 0.04638817

lmY: 0.4856822 +/- 0.046389

Arima: 0.4857 0.0552 8.802 0

@@

lmD: 24.46426 +/- 2.544261

lmY: 24.46465 +/- 2.544306

Arima: 24.4646 3.0718 7.9642 0

@@

lmD: 0.001335923 +/- 0.0001367163

lmY: 0.001335939 +/- 0.0001367188

Arima: 0.0013 2e-04 8.5092 0

@@

lmD: 0.000372438 +/- 6.132797e-05

lmY: 0.0003724446 +/- 6.132906e-05

Arima: 4e-04 1e-04 5.4467 0

@@

lmD: 0.03656094 +/- 0.003621568

lmY: 0.03656157 +/- 0.003621632

Arima: 0.0366 0.0042 8.6966 0

@@

lmD: 0.1872432 +/- 0.2494753

lmY: 0.1872803 +/- 0.2494792

Arima: 0.1718 0.3646 0.4712 0.6375

@@

lmD: 0.0912832 +/- 0.1914519

lmY: 0.09130632 +/- 0.191455

Arima: 0.05 0.3354 0.1491 0.8815

@@

lmD: 0.03034705 +/- 0.02124537

lmY: 0.03034902 +/- 0.02124571

Arima: 0.0304 0.022 1.3788 0.1679

@@

lmD: 6.13936 +/- 4.224962

lmY: 6.139801 +/- 4.22503

Arima: 6.1407 4.3045 1.4266 0.1537

@@

lmD: 0.0005085756 +/- 0.0002811408

lmY: 0.0005085833 +/- 0.0002811453

Arima: 5e-04 3e-04 1.598 0.11

@@

lmD: 0.000398809 +/- 0.0002210804

lmY: 0.0003988093 +/- 0.0002210839

Arima: 4e-04 3e-04 1.4507 0.1469

@@

lmD: 0.008776506 +/- 0.00550671

lmY: 0.008777009 +/- 0.005506798

Arima: 0.0088 0.0057 1.5378 0.1241

@@

@@

\begin{verbatim}
2024-02-28 13:08:49.0 athan@sagan GHI_enh_04_investigate.R 0.269881 mins
\end{verbatim}
